%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah 
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Thomas William Bell} % Your name
%\address{438 Rantz Rd \\ Petawawa, ON \\ K8H 2W8} % Your address
\address{twilliambell97@gmail.com \\ 613-585-1973} % Your phone number and email
\address{twilliambell.wordpress.com \\ GitHub: TWilliamBell}

\begin{document}

\begin{rSection}{Skills}
{\bf $\star$ Advanced analytics skills} (mathematical statistics, optimization, numerical methods, and mechanistic modelling)\\ 
{\bf $\star$ Programming} (scientific and statistical programming in R, Python, and MatLab, key skills for developers such as Git-based version control)\\
{\bf $\star$ Communication} (organizing large groups, writing and speaking to lay and specialist audiences)
\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Masters of Mathematics} \hfill {\em September 2019 - Present} 
\\ Department of Applied Mathematics
\\ University of Waterloo
\\ Cumulative GPA 91\%\\
\\{\bf Bachelors of Science (Honours)} \hfill {\em September 2015 - June 2019} 
\\ Biology and Mathematics
\\ McMaster University
\\ Cumulative GPA 11.1 (rough percentage ~85-90\%)\\
\\{\bf Bachelors of Art} \hfill {\em September 2015 - June 2019}
\\ Philosophy
\\ McMaster University
\\ Philosophy GPA 11.3 (rough percentage: ~85-90\%)

\end{rSection}

\begin{rSection}{Research Work Experience}

{\bf Graduate Research in Mathematical Modelling} \hfill {\em September 2019 - August 2020}

Modelled mitochondrial O$_2$ consumption and ATP generation in rat proximal tubule, medullary thick ascending limb, and hepatocyte cells using ordinary differential equations.  Awarded \$17,500 in my first year by NSERC for this work.

{\bf Undergraduate Research on the Statistics of Sexual Dimorphism} \hfill {\em May 2018 - August 2018}

Conducted a meta-analysis of the relationship between sexual size and shape dimorphism across taxa, requiring the design of non-parametric statistical procedures for the standardized presentation of results.  Awarded \$6000 over 4 months by NSERC (including value matching from McMaster) for this work.

{\bf Undergraduate Research in the History of Philosophy} \hfill {\em May 2017 - August 2017}

Conducted original research on John Locke's work on embodiment.  Awarded \$6000 over 4 months by McMaster University for this work.

\end{rSection}

\begin{rSection}{Non-Research Work Experience}

{\bf Teaching Assistant} \hfill {\em May 2020 - Present}

Instructed tutorials and marked for multiple courses, including several second-year mathematics courses for engineers and mathematicians.

{\bf Tutor} \hfill {\em September 2016 - April 2019}

Tutored students through an online service supported by McMaster's Student Success Centre.

{\bf Teaching Assistant} \hfill {\em October 2017 - April 2018}

Instructed in the Math Help Centre, and marked for two courses, including a second-year mathematics course.

\end{rSection}

\begin{rSection}{Other Research Experience}

{\bf Undergraduate Thesis} \hfill {\em September 2018 - April 2019}

Developed cellular automata models to describe cancer cell proliferation.\\

{\bf Volunteer Research Assistant} \hfill {\em February 2017 - April 2017}

Worked on a meta-analysis of the kidney graft failure literature.

\end{rSection}

\begin{rSection}{Other Relevant Experience}

{\bf Treasurer, McMaster Public Health Association} \hfill {\em September 2017 - April 2019}

Had to coordinate financing and gain access to a couple thousand dollars in funding to organize the Emerging Professionals in Public Health Conference, attended by roughly 60 participants.

{\bf Executive Assistant, McMaster Philosophers' Society} \hfill {\em September 2017 - April 2019}

Organized events and participated in outreach campaigns that doubled our membership over the course of two years.

{\bf Co-President, Effective Altruism Hamilton} \hfill {\em September 2017 - April 2019}

Organized events encouraging participants to think critically about their philanthropic activities.

\end{rSection}

\begin{rSection}{Conference Presentations}

{\bf Mitochondrial Dynamics in the Thick Ascending Limb of the Nephron} \hfill {\em August 2020}

Poster presentation at Dynamics Days Digital 2020.

{\bf A Mathematical Model of Mitochondrial Diseases} \hfill {\em Indefinitely Delayed due to COVID-19}

Accepted contributed lecture to the SIAM/CAIMS Annual Meeting 2020.

{\bf The Humanity of Morality} \hfill {\em April 2019}

Delivered to the Great Lakes Philosophy Conference 2019.

\end{rSection}

%\begin{rSection}{Other Awards}
%
%{\bf President's Graduate Scholarship} \hfill {\em September 2019 - August 2020}
%
%Award value: \$5,000 over one year.
%
%{\bf University Senate Scholarships} \hfill {\em September 2017 - April 2019}
%
%Award value: \$1000 annually over two years.
%\end{rSection}

\begin{rSection}{Memberships in Professional Organizations}

{\bf American Mathematical Society} \hfill {\em December 2020 - Present}

{\bf Society for Industrial and Applied Mathematics} \hfill {\em December 2019 - Present}

Part of the Life Sciences, Dynamical Systems, and Control \& Systems Theory working groups.

\end{rSection}

\begin{rSection}{References}

{\bf Dania Sheaib:} dsheaib@fgcu.edu, (239)-710-9217

{\bf St\'{e}phanie Abo:} sabo@uwaterloo.ca

\end{rSection}

\end{document}